### 2022-08-23 manuscript.Rmd
Adjust figure positions

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.width = 12,
  include = FALSE,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)

>>>>

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.pos = "tp",
  fig.width = 12,
  include = FALSE,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)
